---
title: "qualitative_analysis"
author: "Francesca Tinsdeall"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(dplyr)
library(purrr)
library(stringr)
library(janitor)
library(ggplot2)
library(meta)
library(metafor)
library(dmetar)
library(gridExtra)
library(reshape2)
library(robvis)

```

# Read in correct data 

```{r}
SMD.g <- read.csv('meta.csv')
```


# Risk of Bias assessment 

## Get n of studies falling into low, high or unclear RoB categories for each Risk of Bias assessment question

```{r - rob numbers}

rob <- SMD.g %>% select(study_id_str, ro_b_assessment_blinding_of_animal_carers_handlers, ro_b_assessment_a_priori_power_calculations, ro_b_assessment_blinding_of_outcome_assessors, ro_b_assessment_allocation_concealment, ro_b_assessment_random_housing, ro_b_assessment_baseline_characteristics, ro_b_assessment_incomplete_outcome_data, ro_b_assessment_random_outcome_assessment, ro_b_assessment_unit_of_analysis_error, ro_b_assessment_presence_of_sequence_generation) %>% 
  distinct() %>% 
  select(-study_id_str)

rob.count <- apply(rob, 2 , table)
rob.count
```

### Results 
Blinding of animal handlers: High = 1, Low = 2, Unclear = 45
Blinding of outcome assessors: High = 1, Low = 8, Unclear = 39
Allocation concealment: High = 1, Low = 2, Unclear = 45

A priori power calculations: High = 0, Low = 1, Unclear = 47
Unit of analysis error: High = 26, Low = 21, Unclear = 1
Incomplete outcome data: High = 12, Low = 21, Unclear = 15

Presence of random sequence generation: High = 0, Low = 20, Unclear = 28
Baseline characteristics: High = 0, Low = 6, Unclear = 42
Random housing: High = 1, Low = 1, Unclear = 46
Random outcome assessment: High = 0, Low = 13, Unclear = 35

## Make % studies plot for RoB assessment 
```{r - rob plot}

rob$rob_category <- row.names(rob)
rob_plot <- melt(rob, id.vars = "rob_category") %>% 
  rename("Risk" = "value")
  
rob_plot$variable <- fct_recode(rob_plot$variable, 
                       "Blinding of animal handlers/carers" = "ro_b_assessment_blinding_of_animal_carers_handlers", 
                       'A priori power calculations' = 'ro_b_assessment_a_priori_power_calculations', 
             "Random sequence generation" = "ro_b_assessment_presence_of_sequence_generation",
             "Allocation concealment" = 'ro_b_assessment_allocation_concealment', 
             "Blinding of outcome assessors" = 'ro_b_assessment_blinding_of_outcome_assessors', 
             "Random housing" = "ro_b_assessment_random_housing", 
             "Baseline characteristics" = "ro_b_assessment_baseline_characteristics", 
             "Random outcome assessment" = "ro_b_assessment_random_outcome_assessment", 
             "Incomplete outcome data" =  "ro_b_assessment_incomplete_outcome_data", 
             "Unit of analysis error" = 'ro_b_assessment_unit_of_analysis_error')

rob_plot$Risk <- fct_recode(rob_plot$Risk, 
                            "High RoB" = 'high RoB', 
                            "Low RoB" = 'low RoB',
                            "Unclear RoB" = 'unclear RoB')


rob_plot %>% 
  ggplot(aes(x = variable, fill = Risk)) +
  geom_bar(aes(y = (after_stat(count)/sum(after_stat(count)))*1000)) +
  legend_bottom() +
  coord_flip() + 
  labs(title = "Risk of Bias (RoB) assessment of studies meeting inclusion criteria", x = 'Risk of Bias Assessment Category', y = '% of Studies') +
  theme(plot.title = element_text(size=14, face="bold"))

```


## Power analysis of individual studies to determine whether my meta-analysis has power to detect the pooled effect size

Using https://journals.sagepub.com/doi/10.1177/25152459221147260

Unlikely to be possible because I don't have one effect size per study so probably not compatible with metameta package. Have emailed author. Discuss this as a limitation 


# Getting info for potential moderator variables 
## Sex of animals 

```{r - sex of animals contributing to effect sizes }
sex_of_cohorts_effect <- SMD.g %>% 
  select(effect_id, sex_of_animals) %>% 
  group_by(sex_of_animals) %>% 
  tally()

sex_of_cohorts_effect 
```

```{r - sex of animals within studies}
sex_of_cohorts_study <- SMD.g %>% 
  select(study_id_str, sex_of_animals) %>% 
  distinct() 
  
sex_of_cohorts_study2 <- sex_of_cohorts_study %>% 
  group_by(study_id_str) %>% 
  summarise(N = n()) 

sex_of_cohorts_study <- sex_of_cohorts_study %>% 
  left_join(sex_of_cohorts_study2) %>% 
  mutate(cohorts_in_study = case_when(N == '1' ~ paste(sex_of_animals), 
                                      N == '2' ~ 'male and female independent cohorts')) %>% 
  select(-N) %>% 
  group_by(cohorts_in_study) %>% 
  tally()

```
### Results 
36 effect sizes were from female only cohorts
137 effect sizes were from male only cohorts 
74 effect sizes were from mixed sex cohorts 

5 studies used only female cohorts 
24 studies used only male cohorts 
12 studies assessed males and females in independent cohorts 
13 studies assessed males and females within the same cohort 

## Species of animals 

```{r - species of animals}
species_of_animals_effect <- SMD.g %>% 
  select(effect_id, species_of_animal) %>% 
  group_by(species_of_animal) %>% 
  tally()
```
### Results 
94 effect sizes from mice 
153 effect sizes from rats 


## Strain of animals
```{r - strain of animals}
strain_of_animals_effect <- SMD.g %>% 
  select(effect_id, strain) %>% 
  group_by(strain) %>% 
  tally()
```
### Results 
4 effect sizes from BALB/c
37 effect sizes from C57BL/6
20 effect sizes from C57BL/6J
29 effect sizes from C57BL/6N
4 effect sizes from ddY
41 effect sizes from long-evans 
75 effect sizes from sprague-dawley
31 effect sizes from wistar
6 effect sizes from wistar-hannover 


## PolyI:C Dose administered 
```{r - polyI:C dose administered}
polyIC_effect <- SMD.g %>% 
  select(effect_id, poly_I_C_daily_dose_mg_kg) %>% 
  group_by(poly_I_C_daily_dose_mg_kg) %>% 
  tally()
```
### Results 
3 effect sizes from NA
3 effect sizes from 0.75mg/kg
7 effect sizes from 12mg/kg
12 effect sizes from 2mg/kg
96 effect sizes from 4mg/kg
94 effect sizes from 5mg/kg
3 effect sizes from 8mg/kg
15 effect sizes from 10mg/kg
14 effects zies from 30mg/kg


## Gestational day of polyI:C administration 
```{r - first GD administration}
GD_administration_effect <- SMD.g %>% 
  select(effect_id, GD_first_administration) %>% 
  group_by(GD_first_administration) %>% 
  tally()
```
### Results 
3 effect sizes from NA 
69 effect sizes from GD9
3 effect sizes from GD9.5
3 effect sizes from GD10
11 effect sizes from GD12
1 effect size from GD13
12 effect sizes from GD14
132 effect sizes from GD15
9 effect sizes from GD17
1 effect size from GD17.5
3 effects sizes from GD18

## Route of polyI:C administration 
```{r - administration route}
administration_route_effect <- SMD.g %>% 
  select(effect_id, administration_route) %>% 
  group_by(administration_route) %>% 
  tally()
```
### Results 
58 effect sizes from ip
183 effect sizes from iv 
6 effect sizes from sc


## Postnatal day of %PPI testing 
```{r - PND PPI testing}
PND_PPI_effect <- SMD.g %>% 
  select(effect_id, time) %>% 
  group_by(time) %>% 
  tally()
```
### Results
3 at NA 
5 at PND 30
4 at PND 34
14 at PND35
4 at PND36
6 at PND40
3 at PND 43
2 at PND50
6 at PND51
40 at PND56
22 at PND60
44 at PND70
1 at PND71
1 at PND72
1 at PND73
1 at PND74
2 at PND75
8 at PND76
2 at PND77
2 at PND78
1 at PND79
1 at PND80
1 at PND81
22 at PND84
16 at PND90
16 at PND91
1 at PND92
1 at PND93
1 at PND94
2 at PND97
2 at PND98
3 at PND100
3 at PND112
4 at PND119
2 at PND180

## Developmental stage at %PPI testing 
```{r - dev. stage PPI testing}
stage_PPI_effect <- SMD.g %>% 
  select(effect_id, developmental_stage_PPI) %>% 
  group_by(developmental_stage_PPI) %>% 
  tally()
```
### Results 
3 effect sizes at NA
27 effect sizes from juvenile offspring 
26 effect sizes from adoelscent offspring 
191 effect sizes from adult offspring 


# Qualititaive description of variables not being invetigated as potential moderator variables 











## Put some nice alluvium plots in here (meta-analysis_non.ind)






